### 2014-01-17 Draft/introduction.tex
fixed some reading group comments.

However, most API's do not have formal specifications.
In contrast, API developers commonly describe correct usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
Typically, an API document will describe the both the constraints on that method parameters as well as the constraints in terms of the methods the must be invoked pre/post the current method.
However, formal analysis tools are not designed to work on specifications written in natural languages.

%May be strike out the first sentence 
%May be strike out the term prohibitevely

A na{\"i}ve solution to address the issue, is to manually convert the natural language API description into formal specifications. 
However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web Service API, even before they attempted to formalize the constraints on the method.

@@

%Furthermore, I propose to evaluate the effectiveness of proposed work on real world API's: 1) Java 7 and 2) Amazon S3 REST API. The former is generic language API, while the later is a web based API directed towards cloud-based data storage. The temporal constraints inferred for Java 7 will be compared with the existing approaches to evaluate the effectiveness of proposed work. In contrast, Amazon S3 REST API (relatively recent) representative of the class of API's where neither source code of API nor enough usage examples are available.

%To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
%commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
%Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
%in inferring TT temporal constraints from more than ZZZZ sentences of API documents.

%Software reuse is commonly practiced since the advent of software development~\cite{FrakesIEEETran05}. Software reuse facilitates development of larger, more complex, and timely-delivered software systems~\cite{GaffneySE92}. To determine what and how to reuse, specifications of reusable software libraries play an important role. In the absence of specifications, developers may write code that is inconsistent with the expectations of libraries. As a result, not only such code is of inferior quality and contains faults, the added cost of debugging and correcting such faulty code could also defeat the purpose of reusing software.

>>>>

Despite being desirable, most API's do not have formal specifications.
In contrast, API developers commonly describe correct usage in natural language text in API documents.
Typically, such documents are provided to client-code developers through online access, or are shipped with the API code.
For example, J2EE's API documentation\footnote{\url{http:\\download.oracle.com/javaee/1.7/api/}} is one of the popular API documents.
Typically, an API document will describe the both the constraints on that method parameters as well as the constraints in terms of the methods the must be invoked pre/post the current method.
However, formal analysis tools are not designed to work on specifications written in natural languages.

One way of addressing the issue, is to manually convert the natural language API description into formal specifications. 
However, manually writing formal specifications based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one of the authors more than 10 hours to browse the documentation of one method of a web Service API, even before they attempted to formalize the constraints on the method.

@@

### 2014-01-17 Draft/related.tex
fixed some reading group comments.

// "In contrast" switch up the wording a little bit

Our proposed approach touches a few research areas such as software verification,  NLP on software engineering artifacts, and document augmentation. We next discuss relevant work pertinent to our proposed approach in these areas.

\textbf{Code Contracts - Formal Specifications}
// Define temporal constraints distinction
Design by contracts has been an influential concept in the area of software engineering in the past decade. A significant amount of work has been done in automated inference of code contracts. There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}. Furthermore, there are existing approaches that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries. In contrast, the approach presented in this work infers specifications from the natural language text in API documents, thus complementing these existing approaches when the source code or binaries of the API library is not available.

\textbf{NLP in Software Engineering}

@@

\textit{2. Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents. Their approach uses machine learning to automatically classify such rules. In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well. Furthermore, the performance of the approach is dependent on the quality of the training sets used for ML. In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by these approaches.

@@

\textbf{Augmented Documentation}

Another related field has been that of improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment}. We next describe most relevant approaches. Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives( way of marking the specification sentences) in the default documentation. These directives are highlighted whenever they are displayed in the eclipse environment. Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009}, thus allowing tool based verification. However, a developer has to manually annotate such directives. In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

@@

%\textbf{Program Comprehension}
%
%With respect to program comprehension there are existing techniques that assist in building domain specific ontologies~\cite{Zhou2008}. Furthermore, there are existing approaches~\cite{sridhara2011ICPC,robillard1986schematic} that automatically infer natural language documentation from source code. These approaches would immensely help in comprehension of the functionality of an application. However inherent dependency on source code to generate such documents poses a problem in cases, where source code is not available. We next describe some of these approaches 
%
%\begin{itemize}
% \item Sridhara et al.~\cite{sridhara2011ICPC} use data-flow analysis on the method variables to determine the set of statements that represent the computational intent of the method. The data flow analysis is then used to determine the relation of these statements to the method parameters. These realtions are then thn used to generate the natural language parameter documentation using predefined templates.
%
% \item Zhang et al.~\cite{zhang2011automated} present an approach to generate the explanatory document in the form of code comments explaining the failure of the test case. They first instrument the failing test case. They then use statistical algorithm on the different execution traces of the failing test case to determine a relatively small subset of the suspicious statements along with the objects that need correction for successful execution of test case. Finally, the identified objects that need correction for successful execution of the test case are used to generate the explanatory comments using predefined templates on the generalized properties of the object. For instance, \CodeIn{x == null} becomes \textit{x is set to:null}.
%
% \item Buse et al.~\cite{Buse:2008:ADI:1390630.1390664} use source mining source code repositories to generate usage patterns of an API. They argue that availability of actual usable code examples serves as a better documentation assisting developers in understating the usage of API. They propose the clustering of the uses of an API in the open source repositories based on path information. They then propose type abstraction on the clusters to come up with a usage document. 
%\end{itemize}

>>>>

% "In contrast" switch up the wording a little bit

Our proposed approach touches a few research areas such as software verification,
NLP on software engineering artifacts, and document augmentation.
We next discuss the relevant work pertinent to our proposed approach in these areas.

\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
Design by contracts has been an influential concept in the area of software engineering in the past decade.
A significant amount of work has been done in automated inference of code contracts.
There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}.
Furthermore, there are existing approaches that infer code-contract-like specifications
(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries.
In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.

\subsection{NLP in Software Engineering}

@@

\textit{2. Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents.
Their approach uses machine learning to automatically classify such rules.
In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well.
Furthermore, the performance of the proposed approach is dependent on the quality of the training sets used for ML.
In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by them.

@@

\subsection{Augmented Documentation}

Another related field has been that of improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment}. We next describe most relevant approaches. Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives (way of marking the specification sentences) in the default API documentation. These directives are highlighted whenever they are displayed in the eclipse environment. Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009}, thus allowing tool based verification. However, a developer has to manually annotate such directives. In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

@@
